### 2019-01-02 Sections/economics_of_the_quantum_internet.tex
Game theory update

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_1}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_1}
\end{figure}

@@

The final strategy available to the firms is to consolidate their resources into a distributed cloud computing environment (Sec.~\ref{sec:dist_QC}), where the limitations of a single system are lifted, allowing for even better resource-sharing and improvement beyond what a single system solution can offer. In this scenario, both providers will be able to collaborate such that they can meet their individual computational requirements, without having to fully build independent systems like that in the licensing strategy. Importantly though, while there may be a small loss in utility for one of the parties compared to the licensing strategy, the cooperation allows an overall higher level of utility to be achieved jointly, creating a Nash equilibrium\index{Nash equilibrium} at this point, $C$.

This can be described in the utility payoff matrix outlined in Tab.~\ref{tab:game_theory_1}, where `$\leftarrow/\rightarrow$' indicates the licensing (from/to) strategy, `+' indicates the cloud computing cooperation strategy, and the off-diagonal combinations are the status quo, indicating no cooperation.

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(2.5,2.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_1}
\end{table}

It's important to note that these values are totally arbitrary in nature, and do not have a `real life' interpretation, other than understanding the preferencing of the described strategies. For initial simplicity, the matrix assumes that $A$ and $B$ derive identical utility values from the strategies, resulting in a symmetrical representation of the choices in Fig.~\ref{fig:game_theory_2} around the diagonal axis.

Translating the utility payoff matrix into a graphical representation yields Fig.~\ref{fig:game_theory_2}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_2}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_2}
\end{figure}

@@

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(5,5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_2}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_3}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_3}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_4}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_5}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_5}
\end{figure}

@@

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(2,1.25)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(3,4.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{\comment{To do}}\label{tab:game_theory_3}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_6}
\captionspacefig \caption{\comment{To do}}\label{fig:game_theory_6}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_1}
\captionspacefig \caption{Utility space for two players with access to classical computing.\comment{Vector PDF version please}}\label{fig:game_theory_1}
\end{figure}

@@

The final strategy available to the firms is to consolidate their resources into a distributed cloud computing environment (Sec.~\ref{sec:dist_QC}), where the limitations of a single system are lifted, allowing for even better resource-sharing and improvement beyond what a single system solution can offer. In this scenario, both providers will be able to collaborate such that they can meet their individual computational requirements, without having to fully build independent systems like that in the licensing strategy. Importantly though, while there may be a small loss in utility for one of the parties compared to the licensing strategy, the cooperation allows an overall higher level of utility to be achieved jointly, creating a Nash equilibrium\index{Nash equilibrium} at this point, $C$. This can be described in the utility payoff matrix outlined in Tab.~\ref{tab:game_theory_1}.

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(2.5,2.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{Example of a payoff matrix for two classical computing vendors. `$\leftarrow/\rightarrow$' indicates the licensing (from/to) strategy, `+' indicates the cloud computing cooperation strategy, and the off-diagonal combinations are the status quo, indicating no cooperation.}\label{tab:game_theory_1}
\end{table}

It's important to note that these values are totally arbitrary in nature, and do not have a `real life' interpretation, other than understanding the preferencing of the described strategies. For initial simplicity, the matrix assumes that $A$ and $B$ derive identical utility values from the strategies, resulting in a symmetrical representation of the choices in Fig.~\ref{fig:game_theory_2} around the diagonal axis. Translating the utility payoff matrix into a graphical representation yields Fig.~\ref{fig:game_theory_2}.

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_2}
\captionspacefig \caption{Utility payoff between two players in the classical computing environment.\comment{Vector PDF version please.}}\label{fig:game_theory_2}
\end{figure}

@@

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(3,1.5)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(5,5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{Example utility payoff matrix for quantum computing.}\label{tab:game_theory_2}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_3}
\captionspacefig \caption{Tradeoff in utility between two players in the scenario of quantum computing.}\label{fig:game_theory_3}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_4}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing mixed strategies combining licensing and cloud computing.}\label{fig:game_theory_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_5}
\captionspacefig \caption{Utility tradeoff between two players employing mixed strategies with quantum computers.}\label{fig:game_theory_5}
\end{figure}

@@

\begin{table}[!htbp]
\begin{tabular}{|c|c|c|c|c|}
\hline
Player               & \multicolumn{4}{c|}{$X$}                                            \\ \hline
\multirow{4}{*}{$Y$} & Strategy         & $X\rightarrow Y$ & $X+Y$       & $X\leftarrow Y$ \\ \cline{2-5} 
                     & $X\rightarrow Y$ & $(2,1.25)$        & $(1,1)$     & $(1,1)$         \\ \cline{2-5} 
                     & $X+Y$            & $(1,1)$          & $(3,4.5)$ & $(1,1)$         \\ \cline{2-5} 
                     & $X\leftarrow Y$  & $(1,1)$          & $(1,1)$     & $(1.5,3)$       \\ \hline
\end{tabular}
\captionspacetab \caption{Example utility payoff matrix in the presence of taxation on quantum computers.}\label{tab:game_theory_3}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_6}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing a cloud quantum computing (i.e cooperative) strategy, under the imposition of taxation.}\label{fig:game_theory_6}
\end{figure}
